Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-31 analysis/paper/paper.qmd
replace cv() with mccv() and cvCI() with our custome sharma_cvCI() that uses mccv() instead of CV()

cv <- function(x, ... ) sd(x, ...) / mean(x, ...) *100

#try corrected cv with different methods

library(cvcqv)
ccv <- function(x, ... ) cv_versatile(x, method = "kelly", ...)
mccv <- function(x, ... ) sd(x, ...) / mean(x, ...) *100 * (1 + 1/(4*length(x)))

@@

DFCV <- map_dbl(DF, cv)

#Same as map but better view for summary
cv_all <- map_df(DF, cv)
#arrange the data properly
cv_data_all <- gather(cv_all)

@@

library(MKmisc)
library(purrr)
# CV value
sharma_cv <- function(x,...) cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$estimate*100

#CV sharma interval values
sharma_int_low <- function(x,...) cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$conf.int[1]*100
sharma_int_high <- function(x,...) cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$conf.int[2]*100

>>>>

# cv <- function(x, ... ) sd(x, ...) / mean(x, ...) * 100

# use this one that is optimized for small samples

mccv <- function(x, ... ) sd(x, ...) / mean(x, ...) * 100 * (1 + 1/(4*length(x)))

# BM: this is the cvCI function from https://github.com/stamats/MKmisc, I 
# removed all the non-sharma methods and replaced CV() with mccv() above

sharma_cvCI <- function(x, 
                 conf.level = 0.95, 
                 method = "sharma", 
                 na.rm = FALSE){
    stopifnot(is.numeric(x))

    if(length(conf.level) != 1)
        stop("'conf.level' has to be of length 1 (confidence level)")
    if(conf.level < 0.5 | conf.level > 1)
        stop("'conf.level' has to be in [0.5, 1]")

    alpha <- 1 - conf.level
    zquant <- qnorm(1-alpha/2)
    cv <- mccv(x = x, na.rm = na.rm)
    Infos <- NULL
    if(na.rm) x <- x[!is.na(x)]
    n <- length(x)

     # Sharma and Krishna 1994
      CI.lower <- 1/(1/cv + zquant/sqrt(n))
      CI.upper <- 1/(1/cv - zquant/sqrt(n))
      METH <- "Sharma and Krishna (1994) confidence interval"

    CI <- matrix(c(CI.lower, CI.upper), nrow = 1)
    rownames(CI) <- "CV"
    colnames(CI) <- c(paste(alpha/2*100, "%"), paste((1-alpha/2)*100, "%"))
    attr(CI, "conf.level") <- conf.level
    names(cv) <- "CV"

    return(structure(list("estimate" = cv, "conf.int" = CI, "Infos" = Infos,
                          "method" = METH),
                     class = "confint"))
}
```

```{r}

@@

DFCV <- map_dbl(DF, mccv)

#Same as map but better view for summary
cv_all <- map_df(DF, mccv)
#arrange the data properly
cv_data_all <- gather(cv_all)

@@

library(MKmisc)
library(purrr)
# CV value
sharma_cv <- function(x,...) sharma_cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$estimate*100

#CV sharma interval values
sharma_int_low <- function(x,...) sharma_cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$conf.int[1] * 100

sharma_int_high <- function(x,...) sharma_cvCI(x, conf.level = 0.95, method = "sharma", na.rm = FALSE)$conf.int[2] * 100
